---
title: "Making better spaghetti (plots)"
subtitle: "Exploring the individuals in longitudinal data with the brolgar package"  
author: "<span style = 'font-size: 90%;'>Nicholas Tierney, Monash University</span>"
date: "<span style = 'font-size: 90%;'>YSC, Canerra <br><br> Tuesday 2nd October, 2019 </span><br><br> `r icon::fa('link')` [bit.ly/ysc-njt](https://bit.ly/ysc-njt)<br><br>`r icon::fa('twitter')` [nj_tierney](https://twitter.com/nj_tierney)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [njtheme.css, extra.css]
    nature:
      ratio: "16:9"
      titleSlideClass: ["left", "middle", "inverse"]
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

layout: true
<div class="my-footer"><span>bit.ly/ysc-njt • @nj_tierney</span></div> 

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
# NOTE TO SELF: The CSS styles were created in `create-njt-theme.R`
library(brolgar)
library(tidyverse)
library(visdat)
library(naniar)
library(gganimate)

knitr::opts_chunk$set(
  fig.width = 8,
  fig.height = 4,
  fig.retina = 3,
  fig.align = "center",
  out.width = "90%",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  autodep = TRUE
)

example <- heights %>%
  filter(country == "Australia",
         year >= 1910)
```

---

# What is longitudinal data?

- show a table growing row by row
- unequal measurements

---

# What is longitudinal data?

show plot
--

```{r gg-example, echo = FALSE}
ggplot(example,
       aes(x = year,
           y = height_cm)) + 
  geom_point() + 
  geom_line()
```

---

# What is longitudinal data?

- AKA: "Panel Data" ...,

---

# Now let's add a few more countries

---

# And then a few more...

---

# And all of them?

- watch all of the data get added

---

# We are now in spaghetti Territory!

---

# What do we do?

- plot a sample with `facet_sample()`

---

# What do we want to answer?

---
class: inverse

# Understanding features of your data

## And their role in exploring data

---

# step one: Identifying features means summarising data down to one observation

---

# Step two: Identify which of these features are important / you care about / how to filter 

---

# Step three: You then need to 

---

# Who changes the most?

- use `key_slope`
- 

---



---


# Other example plots

```{r}
heights %>%
  features(height_cm, feat_ranges) %>%
  keys_near(key = country,
            var = range_diff) %>%
  left_join(heights) %>%
  ggplot(aes(x = range_diff,
             y = reorder(country, range_diff))) + 
  geom_point()
```




---
